---
title: "Challenge 1"
format: pdf
editor: source
---

Data needed for this challenge:
  - `athlete_events.csv`
  - `paintings.csv`

## Part 1. The Athlete Dataset

1.  **Read the dataset "athlete_events.csv", and check the first few rows:**

```{r}
# Type your code here
```

2.  **Data Description: Please use the necessary commands and codes and briefly describe this data with a short writing paragraph answering the following questions.**

```{r}
# Type your code here
```

\(1\) What is the dimension of the data (# of rows and columns)?

\(2\) What do the rows and columns mean in this data?

\(3\) What is the unit of observation? In other words, what does each case mean in this data?

\(4\) According to the lecture, is this a "tidy" data?

3.  **Data Transformation: use necessary commands and codes and answer the following questions.**

```{r}
# Type your code here
```

\(1\) How many unique sports, unique teams, and total unique names are in the data?

\(2\) How many years does this data record?

\(3\) Summarize the min, mean, median, and max of "Age" and "Weight". (Must use summarize())

\(4\) (Optional) Summarize the min, mean, median, and max of "Height" by decade.

## Part 2. Paintings

1.  **Read the dataset "paintings.csv".**

```{r}
# Type your code here
```

2.  **Data Description: Please use the necessary commands and codes and briefly describe this data with a short writing paragraph answering the following questions.**

```{r}
# Type your code here
```

\(1\) What is the dimension of the data (# of rows and columns)?

\(2\) What do the rows and columns mean in this data?

\(3\) What is the unit of observation? In other words, what does each case mean in this data?

\(4\) According to the lecture, is this a "tidy" data?

3.  **Data Transformation: use necessary commands and codes, and answer the following questions.**

```{r}
# Type your code here
```

\(1\) How many unique museums are in the data?

\(2\) What are the range and average of the following variable "year"? Must use summarize().

\(3\) How many missing data (NA) are in the following variables: "year" and "depicts"? (tips: use is.na())

\(4\) Which museum have the most paintings of Salvador Dalí?
